---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
knitr::opts_knit$set(global.par = TRUE)
set.seed(1)
```

# greta.gp

<!-- badges: start -->
[![codecov.io](https://codecov.io/github/greta-dev/greta.gp/coverage.svg?branch=master)](https://codecov.io/github/greta-dev/greta.gp?branch=master)
<!-- badges: end -->

### Gaussian processes in greta

`greta.gp` extends greta to let you define Gaussian processes as part of your model. It provides a syntax to create and combine GP kernels, and use them to define either full rank or sparse Gaussian processes.

#### Example

```{r par, echo = FALSE}
par(las = 1, fg = grey(0.7), mar = c(2, 2, 1, 1))
```

```{r simulate, message = FALSE}
# simulate data
x <- runif(20, 0, 10)
y <- sin(x) + rnorm(20, 0, 0.5)
x_plot <- seq(-1, 11, length.out = 200)
```

```{r model, message = FALSE}
library(greta)
library(greta.gp)

# hyperparameters
rbf_var <- lognormal(0, 1)
rbf_len <- lognormal(0, 1)
obs_sd <- lognormal(0, 1)

# kernel & GP
kernel <- rbf(rbf_len, rbf_var) + bias(1)
f <- gp(x, kernel)

# likelihood
distribution(y) <- normal(f, obs_sd)

# prediction
f_plot <- project(f, x_plot)
```

```{r fit, message = FALSE}
# fit the model by Hamiltonian Monte Carlo
m <- model(f_plot)
draws <- mcmc(m)
```

```{r plotting, fig.width = 10, fig.height = 6, dpi = 200}
# plot 200 posterior samples
plot(y ~ x, pch = 16, col = grey(0.4), xlim = c(0, 10), ylim = c(-2.5, 2.5))
for (i in 1:200) {
  lines(draws[[1]][i, ] ~ x_plot,
        lwd = 2,
        col = rgb(0.7, 0.1, 0.4, 0.1))  
}
```

#### Installation

This package depends on version 0.4.2 or higher of [greta](http://greta-stats.org). You can install the latest versions of both packages from GitHub:

```{r install, eval = FALSE}
remotes::install_github("greta-dev/greta")
remotes::install_github("greta-dev/greta.gp")
```
