---
output:
  md_document:
    variant: markdown_github
---

## gretaGP

#### Gaussian processes in greta

gretaGP extends greta to let you define Gaussian processes as part of your model.

##### example
```{r, rng_seed, echo = FALSE}
set.seed(1)
```

```{r, simulate, message = FALSE}
# simulate data
x <- runif(20, 0, 10)
y <- sin(x) + rnorm(20, 0, 0.5)
x_plot <- seq(-1, 11, length.out = 100)
```

```{r, model, message = FALSE}
library (gretaGP)

# hyperparameters
rbf_var = lognormal(0, 1)
rbf_len = lognormal(0, 1)
obs_sd = lognormal(0, 1)

# kernel
k1 <- rbf(rbf_len, rbf_var)  # wiggly kernel
k2 <- bias(1) + linear(1)  # linear kernel
k <- k1 + k2  # combined kernel

# GP, likelihood & predictions
f = gp(x, k, tol = 1e-4)
distribution(y) = normal(f, obs_sd)
f_plot <- project(f, x_plot)
```

```{r fit, message = FALSE}
# fit
m <- model(f_plot)
draws <- mcmc(m, n_samples = 200)
```

```{r plotting}
# plot
plot(y ~ x, pch = 16, col = grey(0.4), xlim = c(0, 10), ylim = range(draws[[1]]))
for (i in 1:200) {
  lines(draws[[1]][i, ] ~ x_plot,
        col = rgb(0.7, 0.1, 0.4, 0.1))  
}
```

##### installation

This package currently depends on the GPflow python package and the gpflowr R package, both of which must be installed before gretaGP will run.

You can install GPflow with pip by typing something like this at a command prompt:

```
git clone https://github.com/GPflow/GPflow.git
cd GPflow && python setup.py install && cd ..
```

You can install gpflowr, the latest version of greta, and this package with the following R commands:

```{r, install, eval = FALSE}
library (devtools)
install_github("goldingn/gpflowr")
install_github("greta-dev/greta")
install_github("greta-dev/gretaGP")
```


[![build status](https://travis-ci.org/greta-dev/gretaGP.svg?branch=master)](https://travis-ci.org/greta-dev/gretaGP)
[![codecov.io](https://codecov.io/github/greta-dev/gretaGP/coverage.svg?branch=master)](https://codecov.io/github/greta-dev/gretaGP?branch=master)
